---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  messages = FALSE,
  warnings = FALSE
)
```

# drpop

<!-- badges: start -->
<!-- badges: end -->

The goal of drpop is to provide users doubly robust and efficient estimates of population size and the condifence intervals for a capture-recapture problem.

## Installation

You can install the released version of drpop from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("drpop")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mqnjqrid/drpop")
```
## Examples

This is a basic example which shows you how to solve a common problem:

```{r example}
library(drpop)

n = 1000
x = matrix(rnorm(n*3, 2, 1), nrow = n)
expit = function(xi) {
  exp(sum(xi))/(1 + exp(sum(xi)))
}
y1 = unlist(apply(x, 1, function(xi) {sample(c(0, 1), 1, replace = TRUE, prob = c(1 - expit(-0.6 + 0.4*xi), expit(-0.6 + 0.4*xi)))}))
y2 = unlist(apply(x, 1, function(xi) {sample(c(0, 1), 1, replace = TRUE, prob = c(1 - expit(-0.6 + 0.3*xi), expit(-0.6 + 0.3*xi)))}))
datacrc = cbind(y1, y2, exp(x/2))[y1+y2 > 0, ]

estim <- popsize(List_matrix = datacrc, func = c("gam"), nfolds = 2, K = 2)
# The population size estimates are 'n' and the standard deviations are 'sigman'
print(estim)
## basic example code
```

The following shows the confidence interval of estimates for a toy data. Real population size is 3000.

```{r plot1, message = FALSE}
library(drpop)

n = 3000
x = matrix(rnorm(n*3, 2,1), nrow = n)

expit = function(xi) {
  exp(sum(xi))/(1 + exp(sum(xi)))
}
y1 = unlist(apply(x, 1, function(xi) {sample(c(0, 1), 1, replace = TRUE, prob = c(1 - expit(-0.6 + 0.4*xi), expit(-0.6 + 0.4*xi)))}))
y2 = unlist(apply(x, 1, function(xi) {sample(c(0, 1), 1, replace = TRUE, prob = c(1 - expit(-0.6 + 0.3*xi), expit(-0.6 + 0.3*xi)))}))
datacrc = cbind(y1, y2, exp(x/2))[y1+y2>0,]

estim <- popsize(List_matrix = datacrc, func = c("gam", "rangerlogit"), nfolds = 2, eps = 0.01)
print(estim)
plotci(estim)
#result = melt(as.data.frame(estim), variable.name = "estimator", value.name = "population_size")
#ggplot(result, aes(x = population_size - n, fill = estimator, color = estimator)) +
#  geom_density(alpha = 0.4) +
#  xlab("Bias on n")

```

The following shows confidence interval of estimates for toy data with a categorical covariate. Real population size is 10000.
```{r plot2, message = FALSE}
library(drpop)
n = 10000
x = matrix(rnorm(n*3, 2, 1), nrow = n)
expit = function(xi) {
  exp(sum(xi))/(1 + exp(sum(xi)))
}
catcov = sample(c('m','f'), n, replace = TRUE, prob = c(0.45, 0.55))

y1 = unlist(apply(x, 1, function(xi) {sample(c(0, 1), 1, replace = TRUE, prob = c(1 - expit(-0.6 + 0.4*xi), expit(-0.6 + 0.4*xi)))}))
y2 = sapply(1:n, function(i) {sample(c(0, 1), 1, replace = TRUE, prob = c(1 - expit(-0.6 + 0.3*(catcov[i] == 'm') + 0.3*x[i,]), expit(-0.6 + 0.3*(catcov[i] == 'm') + 0.3*x[i,])))})
datacrc = cbind.data.frame(y1, y2, exp(x/2), catcov)[y1+y2>0,]

result = popsize_cond(List_matrix = datacrc, condvar = 'catcov')
fig = plotci(result)
fig + geom_hline(yintercept = table(catcov), color = "brown", linetype = "dashed")

```
